---
title: "R practice"
output: html_notebook
---

TODO

* Check our linters
* Using git in Rstudio - better way than terminal?
* Groupby type commands

Key libraries

* ggplot2
* bigrquery
* tibble
* rmarkdown
* dplyr

Resources

* [Pandas R comparison](https://pandas.pydata.org/pandas-docs/stable/getting_started/comparison/comparison_with_r.html)
* [learn X in Y](https://learnxinyminutes.com/docs/r/)
* [ggplot2 book](https://github.com/hadley/ggplot2-book)
* [Advanced R book](http://adv-r.had.co.nz/)
* [Advanced R book chapter on style](http://adv-r.had.co.nz/Style.html)
* [Guide to Rstudio notebooks - like this one!](https://bookdown.org/yihui/rmarkdown/notebook.html)

Datasets
* 
* https://www.kaggle.com/paultimothymooney/how-to-query-the-world-bank-education-data
* https://www.kaggle.com/dipam7/student-grade-prediction

Rmarkdown

* *Cmd+Shift+k* -- preview notebook
* *Cmd+Shift+Enter* -- run code in chunk


R

```{r}
data(cars)
# head(cars) #first 5 rows
# names(cars) #column names
# ?libraryname #help
# library(libraryname) #import
# a <- 4 #assignment
# dim(cars) #dimensions
```

## Tibbles
Improvements on dataframes

```{r}
library(tibble)
cars_tibble <- as_tibble(cars)
cars_tibble["speed"] # filter by column name
```

## Dplyr

Functions like groupby, apply etc
Also the %
```{r}
library(dplyr)
vignette("dplyr")
install.packages("nycflights13")
library(nycflights13)
dim(flights)
```

```{r}
head(flights)
```